### 2021-08-05 paper/paper.tex
Apply some suggestions from code review
Co-authored-by: Hendrik Ranocha <ranocha@users.noreply.github.com>

Some of the main features of \trixi are demonstrated in the following figures.
Figure~\ref{fig:kelvin_helmholtzs} demonstrates entropy-dissipative shock-capturing
methods with adaptive mesh refinement applied to a classical Kelvin-Helmholtz
flow instability problem. Figure~\ref{fig:pressure_waves} shows the approximation
of acoustic perturbation equation~\cite{ewert2003acoustic} wave scattering on a
curvilinear and unstructured domain. The 2D quadrilateral mesh in
Figure~\ref{fig:ginger_mesh} was generated with
HOHQMesh.jl\xspace\footnote{\url{https://github.com/trixi-framework/HOHQMesh.jl}}.

>>>>

Some of the main features of \trixi are demonstrated in the following figures.
Figure~\ref{fig:kelvin_helmholtzs} demonstrates entropy-dissipative shock-capturing
methods with adaptive mesh refinement applied to a classical Kelvin-Helmholtz
flow instability problem. Figure~\ref{fig:pressure_waves} shows the approximation
of acoustic perturbation equations~\cite{ewert2003acoustic} wave scattering on a
curvilinear and unstructured domain. The 2D quadrilateral mesh in
Figure~\ref{fig:ginger_mesh} was generated with
HOHQMesh.jl\xspace\footnote{\url{https://github.com/trixi-framework/HOHQMesh.jl}}.
